### 2014-12-12 paper.tex
new section: legislative and legal changes

@@

  \subsection{Court Test Threshold}
  10\% for areas w/at least 3 districts, include compactness considerations.  if close on one, consider the other
  \subsection{Policy Recommendations}
  Use nonpartisan methods

>>>>

  \section{Legislative and Legal Changes}

  Based on the data we have gathered, we propose the following court tests.  At a congressional level, districting plans for states with at least 3 districts are illegal if:
  \begin{itemize}
  \item A state plan has a voter efficiency gap greater than 20\% OR
  \item A state plan has a seat gap of greater than two seats OR
  \item%TODO: pick a compactness threshold, or a way to integrate in compactness
  \end{itemize}

  We believe that this accurately captures the most egregious of gerrymandering, as for states with at least 3 congressional districts, a 20\% threshold limit or 2 seat gap creates a balance to test for gerrymandering in both small and large states.  For small states, this could mean a seat distribution changing from 3-0 to 2-1, which is small on the grand scale, but possibly offers better representation within that state. Likewise, it can catch large states, who can have a strong influence on the overall makeup of Congress.  Based on our data, it would invalidate districting plans in Florida, Michigan, New Jersey, North Carolina, Ohio, Pennsylvania, Texas, and Virginia on the basis that they have a gap larger than two seats, and Connecticut and Nebraska, on the basis of having greater than a 20\% efficiency gap. Providing this criteria will allow the courts to effectively decide on gerrymandering cases.\\

  We also propose that states revise their policy on allowing state legislatures to draw lines independently.  Nonpartisan and balanced partisan processes create fair, consensus plans, as they will require agreements that prevent the parties from simply passing a partisan bill designed to reduce the prevalence of partisan gerrymandering.

@@
